### 2019-04-21 monograph/thesis/chapters/introduction.tex
Removed the template monograph/thesis/postexto/apendice_a.tex
Enabled the \addGoToSummary and translated the first paragraphs on
monograph/thesis/chapters/introduction.tex

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\phantomsection

@@

    The work first part will be based on research in
    articles, books, theses, dissertations, trusted authors websites,
    and through new demonstrated evidences based on arguments
    in the monograph evolution.
    Also, present results after building a new tool
    which proposes a solution for the problems presented and detailed.

    In this proposal last chapter which lies on the part
    called `\nameref{sec:software_implementation}', which holds the implementation of a
    tool for code `Beautifying'.

    \section{Context}

    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{naturalCodingConventions}

>>>>

@@

\lang{
    The work first part will be based on research in
    articles, books, theses, dissertations, trusted authors websites,
    and through new demonstrated evidences based on arguments
    in the monograph evolution.
    Also, present results after building a new tool
    which proposes a solution for the problems presented and detailed.
}{
    A \hyperref[sec:primeira_parte]{primeira parte} deste trabalho será baseado em artigos,
    livros, outras dissertações,
    sites confiáveis e por novas evidências demonstradas no desenvolvimento deste trabalho.
}

\lang{
    In this proposal last chapter which lies on the part
    called `\nameref{sec:segunda_parte}', which holds the implementation of a
    tool for code `Beautifying'.
}{
    E finalmente,
    na \hyperref[sec:segunda_parte]{segunda parte} deste trabalho,
    será apresentada a sugestão e implementação de uma ferramenta.
}

\section{\lang{Context}{Contexto}}

\lang{
    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{naturalCodingConventions}
}{
    Perguntas como ``O quê são boas práticas de programação'' não são fáceis de responder.
    Cada programador aprende a escrever seu códigos de uma determinada maneira,
    seja utilizando 2, 4,
    ou 8 espaços para criar blocos de indentação,
    ou sempre deixar uma linha em branco antes de estruturas de controle como if\s,
    while\s, etc. \cite{naturalCodingConventions}
}
